Flatiron cleaning

### 2021-10-08 Rmd/rdi analysis.Rmd
Fix bug removing line and clean interval of data to bind

tbl10 <- Frontline %>%
  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Neoadjuvant")
tbl10 <- tbl10 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl11 <- Frontline %>%
  filter(str_detect(drugname, "taxel") & chemotherapy_type == "Adjuvant")
tbl11 <- tbl11 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
# tbl12 <- Frontline %>%
#   filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
# tbl12 <- tbl12 %>%
#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl10, tbl11),
          group_header = c("taxel/Neoadjuvant", "taxel/Adjuvant")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>

>>>>

tbl10 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Neoadjuvant")
tbl10 <- tbl10 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl10$month_at_os, event = tbl10$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl11 <- Frontline %>%
  filter(str_detect(drugname, "protein") & chemotherapy_type == "Adjuvant")
tbl11 <- tbl11 %>%
  select(vitalstatus, RDI_grp, RDI_grp1) %>%
  tbl_uvregression(method = survival::coxph,
                 y = (Surv(time = tbl11$month_at_os, event = tbl11$vitalstatus)),
                 exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent() %>%
  modify_header(update = list(label ~ "**paclitaxel/Adjuvant**"))
# tbl12 <- Frontline %>%
#   filter(str_detect(drugname,"taxel") & str_detect(chemotherapy_type, "Chemo"))
# tbl12 <- tbl12 %>%
#   select(vitalstatus, RDI_grp, RDI_grp1) %>% tbl_uvregression(method = survival::coxph,
#                  y = (Surv(time = tbl12$month_at_os, event = tbl12$vitalstatus)),
#                  exponentiate = TRUE) %>% bold_p(t = .05) %>% add_nevent()
tbl_stack(list(tbl10, tbl11),
          group_header = c("PPB/Neoadjuvant", "PPB/Adjuvant")) %>%
  bold_labels() %>%
  italicize_levels()
```
<br>
<br>
